Visualizations for article

### 2015-12-02 101-visualizations-for-article.Rmd
State to state network visualization

```{r message=FALSE}
library("readr")
library("igraph")
library("dplyr")
library("stringr")
library("parallel")
library("scales")
library("textreuse")
source("R/best-section-matches.R")
source("R/summarize-borrowings.R")
source("R/extract-date.R")
source("R/extract_code_names.R")
options("mc.cores" = 6L)
```

@@

>>>>

```{r message=FALSE}
library("readr")
library("igraph")
library("dplyr")
library("stringr")
library("parallel")
library("scales")
library("textreuse")
source("R/best-section-matches.R")
source("R/summarize-borrowings.R")
source("R/extract-date.R")
source("R/extract_code_names.R")
source("R/extract-state.R")
options("mc.cores" = 6L)
```

@@

Now do a state to state network:

```{r}
min_state_borrowings <- 100
top_matches <- 3
edges_states <- code_match_summary %>% 
  mutate(borrower_date = extract_date(borrower_code),
         match_date = extract_date(match_code),
         borrower_state = extract_state(borrower_code),
         match_state = extract_state(match_code)) %>% 
  filter(!is.na(match_code),
         borrower_date >= match_date,
         borrower_state != match_state) %>% 
  group_by(borrower_state, match_state) %>% 
  summarize(n = sum(n)) %>% 
  filter(n >= min_state_borrowings) %>% 
  select(borrower_state, match_state, weight = n) %>% 
  group_by(borrower_state) %>% 
  top_n(top_matches, weight) %>% 
  ungroup() %>% 
  mutate(weight = rescale(weight))

edges_states

g_states <- graph_from_data_frame(edges_states, directed = TRUE)

state_distances <- distances(g_states, to = "NY", algorithm = "unweighted") 
nodes_states <- data_frame(name = rownames(state_distances),
                           distance = state_distances[, 1]) %>% 
  mutate(color = ifelse(distance == 0, "red",
                        ifelse(distance == 1, "green",
                               ifelse(distance == 2, "yellow", "lightblue"))))

g_states <- graph_from_data_frame(edges_states, directed = TRUE,
                                  vertices = nodes_states) %>% 
  decompose(min.vertices = 3) %>% 
  `[[`(1)

set.seed(4221)
g_states <- g_states %>% add_layout_(with_graphopt(niter = 4000,
                                                   spring.length = 25),
                                     normalize())
par(mar = c(0,0,1,0))
plot(g_states, 
     edge.width = edge_size_clamp(g_n), edge.arrow.size = 0.5,
     edge.arrow.mode = 1,
     vertex.size = 5, vertex.label.dist = 0.85, vertex.label.degree = pi)
title("Borrowings between states, number of sections borrowed")
```
